Flexibility of interactions depends on habitat suitability

### 2019-09-01 paper/manuscript.Rmd
Some comments for the discussion

We found a positive association between environmental suitability and the niche breath. 
This relationship was maintained when we account for the overall generality of a species and even in extremely conservative model parametrization when we include the number of possible interacting species as an independent variable. 
We define "possible" interacting species as one with which the species interacts in any of our ecological communities.

No interaction significant between guild and relationship which highlights that differences are rooted in eco-evolutionary processes rather than behaviour.

Relationship is even stronger when we only include species for which we have more info. i.e. in more that 5 communities.

<!-- We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004).  -->
<!-- We learnt that there is a trade-off pollination dynamics (Cagua in review?). -->
<!-- This means that species with more environemntal favours are better prepared to deal with the trade-offs that pollination can convey. Cool! -->

>>>>

<!-- We found a positive association between environmental suitability and the niche breath. 
This relationship was maintained when we account for the overall generality of a species and even in extremely conservative model parametrization when we include the number of possible interacting species as an independent variable. 
We define "possible" interacting species as one with which the species interacts in any of our ecological communities.  -->

<!-- No interaction significant between guild and relationship which highlights that differences are rooted in eco-evolutionary processes rather than behaviour.  -->

<!-- Relationship is even stronger when we only include species for which we have more info. i.e. in more that 5 communities.  -->

<!-- Environment can also affect neitral process because it affects encounter rates between species.
This can happen either through changes in abundance driven by patterns of temporal or spatial overlap or through changes in the search efficiency.  -->
<!-- We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004).  -->
<!-- We learnt that there is a trade-off pollination dynamics (Cagua in review?). -->
<!-- This means that species with more environemntal favours are better prepared to deal with the trade-offs that pollination can convey. Cool! -->
